Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-06-11 paper/ms.tex
Tidy up cumulative yield distribution figure
Switch colors to be more consistent with Don's choice in his 2016 paper.
Use my matplotib so that tex works and style is more formal.
Made a data collection script and included data for figure
(plotscript was previously doing the collection from the individual runs
every time.)
Included the collection script here.
Update and swap color in IGE v dens mass fig
also add results from Don's paper for comparison.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.pdf}
\caption{\label{fig:cumdist}
The cumulative distribution of the final \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models. The hybrid results are shown in red, and the CO
results are shown in blue. The curve for the hybrid models is shifted
to the left, indicating that explosions from hybrid progenitors produce
less \Ni{56} than explosions from traditional C-O models.
}
\end{figure}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models is presented in Figure \ref{fig:cumdist}.
The figure shows that the hybrid models consistently have a higher
cumulative fraction at a given mass of \Ni{56}, which indicates
that the yields of \Ni{56} are consistently lower in explosions
from hybrid progenitors. {\color{red} CHECK/EXPAND THIS}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens.pdf}
\caption{\label{fig:masshighdens}
Final estimated IGE {\color{red}
TO BE SURE- NOT \Ni{56} AS FIGURE IS LABELED?} yield
vs.\ mass {\color{red} above} $2\times 10^7~\grampercc$
at the time of the first DDT in a simulation.  Individual
realizations are shown (C-O-Ne
progenitors in red, C-O in blue) along with rectangles of length
$\pm 1 \sigma$ along each axis and centered at their average values
for C-O and C-O-Ne.
}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{figures/cum_dis_Ni56.pdf}
\caption{\label{fig:cumdist}
The cumulative distribution of the final \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models. The hybrid results are shown in red, and the CO
results are shown in blue. The curve for the hybrid models is shifted
to the left, indicating that explosions from hybrid progenitors produce
less \Ni{56} than explosions from traditional C-O models.
}
\end{figure}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models is presented in Figure \ref{fig:cumdist}.
The figure shows that the hybrid models consistently have a higher
cumulative fraction at a given mass of \Ni{56}, which indicates
that the yields of \Ni{56} are consistently lower in explosions
from hybrid progenitors. {\color{red} CHECK/EXPAND THIS}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ige_v_mass_at_high_dens.pdf}
\caption{\label{fig:masshighdens}
Final IGE yield
vs.\ mass above $2\times 10^7~\grampercc$
at the time of the first DDT in a simulation.  Individual
realizations are shown (C-O-Ne
progenitors in blue, C-O in red) along with rectangles of length
$\pm 1 \sigma$ along each axis and centered at their average values
for C-O and C-O-Ne.  Similar rectangles found in W16 for a progenitor without
mixing during cooling are shown in a lighter shade with dashed borders.
}
\end{figure}
